A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-11 paper.tex
get most todos done

% other relations
\newcommand{\tailable}[2]{\ensuremath{\casttyping{!}{#1}{#2}}}
\newcommand{\consistent}[2]{\ensuremath{#1\sim#2}}
\newcommand{\shallowlyconsistent}[2]{\ensuremath{#1\smile#2}}
\newcommand{\notshallowlyconsistent}[2]{\ensuremath{#1\not\smile#2}}
\newcommand{\expressiontyping}[3]{\ensuremath{#1 \vdash #2 : #3}}
\newcommand{\matching}[2]{\ensuremath{#1 \triangleright #2}}
\newcommand{\valuetyping}[2]{\ensuremath{\vdash #1 : #2}}
\newcommand{\envtyping}[2]{\ensuremath{#1 \vdash #2}}
\newcommand{\casttyping}[3]{\ensuremath{\vdash #1 : #2 \Longrightarrow #3}}
\newcommand{\transitivelyreducetoM}[3]{\ensuremath{#2 \longmapsto_{#1}^{*} #3}}
\newcommand{\transitivelyreduceto}[2]{\ensuremath{#1 \longmapsto^{*} #2}}
\newcommand{\transitivelyreducetoD}[2]{
	\ensuremath{#1 \longmapsto_{\LDMachine}^{*} #2}}
\newcommand{\transitivelyreducetoUD}[2]{
	\ensuremath{#1 \longmapsto_{\LUDMachine}^{*} #2}}
\newcommand{\reduceto}[2]{\ensuremath{#1 \longmapsto #2}}
\newcommand{\reducetoR}[3]{\ensuremath{#2 \longmapsto_{\CMachine{#1}} #3}}
\newcommand{\reducetoD}[2]{\reducetoR{\BLD}{#1}{#2}}
\newcommand{\reducetoUD}[2]{\reducetoR{\BLUD}{#1}{#2}}
\newcommand{\reducetoS}[3]{\ensuremath{#2 \longmapsto_{\SMachine{#1}} #3}}
\newcommand{\evalto}[2]{\ensuremath{\mathrm{eval}(#1)=#2}}
\newcommand{\withmachineevalto}[3]{\ensuremath{\mathrm{eval}_{#1}(#2)=#3}}
\newcommand{\evaltoR}[3]{\ensuremath{\mathrm{eval}_{\CMachine{#1}}(#2)=#3}}
\newcommand{\evaltoD}[2]{\evaltoR{\BLD}{#1}{#2}}
\newcommand{\evaltoUD}[2]{\evaltoR{\BLUD}{#1}{#2}}
\newcommand{\evaltoS}[3]{\ensuremath{\mathrm{eval}_{\SMachine{#1}}(#2)=#3}}
\newcommand{\compatibletailhead}[2]{\ensuremath{#1\;R\;#2}}
\newcommand{\goodgap}[1]{\ensuremath{\mathrm{good}(#1)}}
\newcommand{\compileto}[4]{\expressiontyping{#1}{#2\rightsquigarrow#3}{#4}}
\newcommand{\machineequiv}[2]{
	\ensuremath{
		\withmachineevalto{#1}{e}{o}	
		\text{ if and only if }
		\withmachineevalto{#2}{e}{o}
		\text{ for all }
		\expressiontyping{\emptyset}{e}{T}
		\text{ and }
		\valuetyping{o}{T}
	}}
\newcommand{\bisimE}[3]{\ensuremath{#1 \vdash #2 \approx #3}}
\newcommand{\bisimv}[3]{\valuetyping{#1 \approx #2}{#3}}
\newcommand{\bisimr}[3]{\valuetyping{#1 \approx #2}{#3}}
\newcommand{\bisimF}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisimc}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisimK}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisims}[3]{\valuetyping{\ensuremath{#1 \approx #2}}{#3}}

@@

\todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
\todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
sentence. It might be appopriate to cite it elsewhere in the paper. Also,
there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
\todo[inline]{KC: How about citing the origin of the proxy-based approach when we talk
about the CPSed even-odd example?
I am confused about which paper to cite. \cite{herman2010space} seems to be citing
\cite{findler2002contracts} for the proxy-based approach of casting function.
Here is the relevant sentences from \cite{herman2010space}:
``In general, it is not possible to check if an untyped function satisfies a
particular static type. A natural solution is to wrap the function in a proxy that, whenever
it is applied, casts its argument and result values appropriately, ensuring that the function
is only observed with its expected type. This proxy-based approach was formalized by Findler
and Felleisen [15] ...''
I am \textit{not} trying to say I don't believe in your statements about the origins of
the proxy-based approach and blame tracking in functions.
I want to know whether \citet{herman2010space} is citing the right paper.
Maybe both papers came up independently with a similar idea but \cite{findler2002contracts}
is more related to our work.
}

\todo[inline]{JS: In the above you've lumped proxy-based and blame
  tracking together, which is incorrect. AFAIK,
  \cite{findler2002contracts} is the origin of blame tracking. AFAIK,
  \citet{Breazu-Tannen:1990vc} is the origin of proxy-based casts.
  You can read both papers for yourself and be the judge.  BTW, TAPL
  (section 15.6) cites Breazu-Tannen.  So \citet{herman2010space}
  cited the wrong paper for function proxies, perhaps because they
  didn't know about \citet{Breazu-Tannen:1990vc}. Also,
  \cite{findler2002contracts} should have cited
  \citet{Breazu-Tannen:1990vc} but did not. Perhaps because they did
  not consider that papers about ``casts'' to be closely related to
  their paper about ``contracts''.  Or perhaps they too did not know
  about \citet{Breazu-Tannen:1990vc}.  Authors make mistakes all the
  time regarding related work, and this is just yet another example of
  that. For that matter, I should have cited
  \citet{Breazu-Tannen:1990vc} in \citet{siek2006gradual} but did not,
  probably because I had learned about it from TAPL and therefore
  thought it was so standard that it didn't need a citation.  But it
  would have been better for me to cite it.}

@@

Continuations are not the only place where casts can accumulate.
Consider a variant of the above program written in
continuation-passing style.  Here, both functions returns
\lstinline|Bool| so there is no implicit cast in tail position.
However, the argument \lstinline|k| is wrapped in a cast in each
recursive call because the type of \lstinline|k| is less precise in
\lstinline|even?| than it is in \lstinline|odd?|.
\begin{lstlisting}
(define (even? [n : Int] [k : (-> $\star$ Bool)]) : Bool
  (if (= n 0) (k #t) (odd? (- n 1) k)))
(define (odd? [n : Int] [k : (-> Bool Bool)]) : Bool
  (if (= n 0) (k #f) (even? (- n 1) k)))
\end{lstlisting}
These example programs are adapted from those of Herman et al.~\citep{herman2010space}.
We direct readers to their work for more examples and a detailed explanation.

@@

Of course, a space-efficient cast representation must be proved
correct. That is, a language implementation that uses space-efficient
casts should give the same output as the language semantics. Our
generic CEK machine comes with generic theorems mechanized in
the Agda proof assistant~\citep{norell2008dependently}
(Section~\ref{sec:framework}) that researchers can use to prove a cast
representation correct.  We believe this framework can reduce the
burden of proving correctness theorems and help people focus on the
cast representations. As a demonstration, we apply the framework to
Lazy UD coercions in normal form~\citep{Siek:2015:BCT:2737924.2737968}
and Lazy UD threesomes~\citep{Siek:2010:TWB:1706299.1706342}. We
believe the framework is also applicable to other cast
representations. The framework and demonstrations are available at the
following URL:
\[\text{\urlFrameworkAndIllustration}\]
\todo[inline]{KC: is this the right place to mention that in Agda
code we use de Bruijn indexes?}
\todo[inline]{JS: no, that's too deep into the details for the introduction
   of a paper that is not about variable representations.}

@@

\todo[inline]{JS: add a sentence that summarizes this section,
  mentioning the topics of the two subsections.}

\subsection{Dynamics semantics parameterized over cast representations}

@@

\citet{garcia2014deriving} presents a dynamic semantics for the Eager
D blame strategy, using coercions. They claim that ``the artefacts for
coercions can be replaced by other artefacts implementing different
dynamic semantics''.

\todo[inline]{JS: The above is too short of a description of that related
work.}
\todo[inline]{KC: I am actually very confused by \citet{garcia2014deriving}.
They stated that ``Theorems 8.1 and 8.3 can be generalised for other choices
of dynamic semantics by applying the correspondence described
through the paper starting with a different set of coercion artefacts.''.
However they didn't give a generalization and it is unclear to me over what
their system is parameterized (cast representations? apply-coercion and seq?.}
\todo[inline]{JS: your comment above says what you should say
  (except the part about your confusion). Say it in a matter-of-fact
way, and not a derogitory way.}

\subsection{Correctness of cast representations}

@@

\cite{Siek:2015:BCT:2737924.2737968} proves the correctness
of \LUD\ coercions in normal form. Their approach is similar to
that of \citet{Siek:2010:TWB:1706299.1706342}. They defines
three calculi (i.e. $\lambda B$ and $\lambda C$ and $\lambda S$). 
$\lambda B$ is the blame calculus. 
$\lambda C$ uses coercions but doesn't normalize coercions
so is not space-efficient. $\lambda S$ uses coercions in normal form
and is space-efficient. To establish the correctness of
their cast representation,
they prove a bisimulation relating $\lambda B$ to $\lambda C$
and a bisimulation relating $\lambda C$ to $\lambda S$.
Inspired by the approaches of \cite{Siek:2010:TWB:1706299.1706342}
and \cite{Siek:2015:BCT:2737924.2737968}, 
we also use the bisimulation technique.
\todo[inline]{JS: there is a least one interesting difference regarding
  the bisimulation: your lemma 3 has an ``upto reduction'' flavor to it
  which makes your $\approx$ relation simpler. }

@@

@@

\caption{Bisimulation between \CBMachine\ and \SMachine{C}. It is the
  smallest congruence relation containing the shown rules. Everything
  to the left of $\approx$ is in \CBMachine{} and everything to the
  right is in \SMachine{C}.}
\label{fig:bisim-SC-D}
\end{figure}

@@

% \begin{lemma}[Lazy D Weak Bisimulation between \LDMachine\ and \SMachine{C}]
% 	\label{lem:weak-bisim-SC-D}
% 	Assume $C$ implements Lazy D Cast ADT
% 	and $s_1$ is a state in \LDMachine\
% 	and $s_1'$ is a state in \SMachine{C}
% 	and $\bisims{s_1}{s_1'}{T}$
% 	then either
% \begin{enumerate}
% \item $s_1  = \error{l}$
%   and $s_1' = \error{l}$
%   for some $l$, or
% \item $s_1 = \shalt{v}$
%   and $s_1' = \shalt{v'}$
%   and $\bisimv{v}{v'}{T}$
%   for some $v$ and $v'$, or
% \item $\reduceto{s_1}{^{+}s_2}$
%   and $\reduceto{s_1'}{^{+}s_2'}$
%   and $\bisims{s_2}{s_2'}{T}$
% \end{enumerate}
% \end{lemma}
% %\begin{proof}
% %We proceed by case analysis on $\bisims{s_1}{s_1'}{T}$. 
% %\begin{description}
% %\item[Case $\inference{
% %}{
% %	\bisims{\error{l}}{\error{l}}{T}
% %}$]
% %This is case (1).
% %\item[Case $\inference{
% %	\bisimv{v}{v'}{T}
% %}{
% %	\bisims{\shalt{v}}{\shalt{v'}}{T}
% %}$]
% %This is case (2).
% %\item[Case $\inference{
% %	\expressiontyping{\Gamma}{e}{T} \\
% %	\bisimE{\Gamma}{E}{E'} \\
% %	K \approx K' : T
% %}{
% %	\bisims{\sexpr{e}{E}{K}}{\sexpr{e}{E'}{K'}}{T}
% %}$]
% %This is case (3). By case analysis on $e$.
% %\item[Case $\inference{
% %	\bisimv{v}{v'}{S} \\
% %	\bisimK{K}{K'}{S}{T}
% %}{
% %	\bisims{\scont{v}{K}}{\scont{v'}{K'}}{T}
% %}$]
% %This is case (3). By inversion on $\bisimK{K}{K'}{S}{T}$, we have
% %\[
% %\begin{array}{rcl}
% %K  & = &
% %\Kcons{
% %	\Fcast{\ccast{S_1}{l_1}{S_2}}
% %}{\ldots\Kcons{\Fcast{\ccast{S_{n-1}}{l_{n-1}}{S}}}{K_1}} \\
% %K' & = &
% %\Kcons{\Fcast{c'}}{k_1'}
% %\end{array}
% %\]
% %After zero or more transition steps, $\scont{v}{K}$ will either transition to 
% %$\scont{u}{K_1}$ for some $u$ or transition to $\error{l}$ for some $l$ if one 
% %of the cast fail. On the \SMachine{C} side, $\scont{v'}{K'}$ will either 
% %transition to $\applyCont{u'}{k_1'}$ for some $u'$ or transition to 
% %$\error{l'}$ for some $l'$ if the cast fail. Because the sequence of casts in 
% %$K$ bisimulates the cast in $K'$, we can show with  
% %Lemma~\ref{lem:LazyD-apply-cast-preserve-bisim} that either
% %\begin{itemize}
% %	\item all casts succeed and	$\bisimv{u}{u'}{S}$, or
% %	\item both machines transition to error state and $l = l'$
% %\end{itemize}
% %When all casts succeeded, we also have $\bisimK{K_1}{k_1'}{S}{T}$ and need to 
% %show that $\reduceto{\scont{u}{K_1}}{s_2}$ and $\applyCont{u'}{k_1'} = s_2'$ 
% %and $\bisims{s_2}{s_2'}{T}$ for some $s_2$ and $s_2'$.
% %%
% %We proceed by case analysis on $K$. The most interesting cases 
% %are function application and pair projection. Due to space limitation, 
% %we only illustrate the general idea with function applications
% %
% %\begin{description}
% %\item[Subcase $\infr{
% %	\bisimv{v_1}{v_1'}{\Pfunc{S}{T_1}} \qquad
% %	\bisimK{K_2}{K_2'}{T_1}{T}
% %}{
% %	\bisimK{
% %		\Kcons{\FappOX{v_1}}{K_2}
% %	}{
% %		\Kcons{\FappOX{v_1'}}{K_2'}
% %	}{S}{T}
% %}$] By inversion on $\bisimv{v_1}{v_1'}{\Pfunc{S}{T_1}}$ we know the proxies 
% %in $v_1$ bisimulate the proxies in $v_1'$. After a reasoning similar to the 
% %above one that we used to reason about casts in continuations, we know that 
% %either both machines will transition to error states if the input proxies fail 
% %in casting the argument, or both machines will transition to a state 
% %evaluation 
% %the function body.
% %\todo{need to elaborate this part, or just delete it.}
% %\end{description}
% %\end{description}
% %\end{proof}

% \begin{lemma}[Lazy UD Weak Bisimulation between \LUDMachine\ and \SMachine{C}]
% 	\label{lem:weak-bisim-SC-UD}
% 	Assume $C$ implements Lazy UD Cast ADT
% 	and $\bisims{s_1}{s_1'}{T}$
% 	then either
% 	\begin{enumerate}
% 		\item $s_1  = \error{l}$
% 		and $s_1' = \error{l}$
% 		for some $l$, or
% 		\item $s_1 = \shalt{v}$
% 		and $s_1' = \shalt{v'}$
% 		and $\bisimv{v}{v'}{T}$
% 		for some $v$ and $v'$, or
% 		\item $\reduceto{s_1}{^{+}s_2}$
% 		and $\reduceto{s_1'}{^{+}s_2'}$
% 		and $\bisims{s_2}{s_2'}{T}$
% 	\end{enumerate}
% \end{lemma}
% \begin{proof}
% 	Similar to Lemma~\ref{lem:weak-bisim-SC-D}.
% \end{proof}

\todo[inline]{JS: There should be some text regarding the following
two theorems.}
\todo[inline]{KC: will do}

\begin{theorem}[Correctness of Lazy D \SMachine{C}]
	\label{thm:SD-equiv}
	Suppose $C$ is a Lazy D Cast ADT.
	\[
	\machineequiv{\CBMachine}{\SMachine{C}}
	\]
\end{theorem}
% \begin{proof}
% 	By the definitions of $\textit{eval}$, we need to show 
% 	\[
% 	\transitivelyreducetoM{\CMachine{B}}{\sexpr{e}{\emptyset}{\Knil}}{
% 		s
% 	}
% 	\;\text{if and only if}\;
% 	\transitivelyreducetoM{\SMachine{C}}{\sexpr{e}{\emptyset}{\mkCont{\Knil}}}{
% 		s'
% 	}
% 	\]
% 	where $s$ and $s'$ are bisimuated final states, i.e. of the form 
% 	$\shalt{v}$ or $\error{l}$. The initial states are related by the 
% 	bisimulation relation, so we can prove this theorem with 
% 	Lemma~\ref{lem:weak-bisim-SC-D}.
% \end{proof}

\begin{theorem}[Correctness of Lazy UD \SMachine{C}]
	\label{thm:SUD-equiv}
	Suppose $C$ is a Lazy UD Cast ADT.
	\[
	\machineequiv{\CBMachine}{\SMachine{C}}
	\]
\end{theorem}
% \begin{proof}
% 	Similar to Theorem~\ref{thm:SD-equiv}.
% \end{proof}

@@

Subsection~\ref{sec:LazyD-Hypercoercions} implements the \CastADT{}
with the \LD{} hypercoercions and proves that \LD{} hypercoercions is
a Lazy D Cast ADT.  Subsection~\ref{sec:LazyUD-Hypercoercions} does
the same for \LUD{}.  Finally, we argue in
Subsection~\ref{sec:hypercoercions-compact} that hypercoercions
consume less space than coercions in normal form and hence are more
suitable for implementation.

@@

\figref{fig:LazyD-Hypercoercions-composition} defines the composition
operator \compose{c}{c} for \LD\ hypercoercions and
\figref{fig:aux-hypercoercion-composition} defines some auxilliary
predicates and functions.

>>>>

% other relations
\newcommand{\tailable}[2]{\ensuremath{\casttyping{!}{#1}{#2}}}
\newcommand{\consistent}[2]{\ensuremath{#1\sim#2}}
\newcommand{\shallowlyconsistent}[2]{\ensuremath{#1\smile#2}}
\newcommand{\notshallowlyconsistent}[2]{\ensuremath{#1\not\smile#2}}
\newcommand{\expressiontyping}[3]{\ensuremath{#1 \vdash #2 : #3}}
\newcommand{\matching}[2]{\ensuremath{#1 \triangleright #2}}
\newcommand{\valuetyping}[2]{\ensuremath{\vdash #1 : #2}}
\newcommand{\envtyping}[2]{\ensuremath{#1 \vdash #2}}
\newcommand{\casttyping}[3]{\ensuremath{\vdash #1 : #2 \Longrightarrow #3}}
\newcommand{\transitivelyreducetoM}[3]{\ensuremath{#2 \longmapsto_{#1}^{*} #3}}
\newcommand{\transitivelyreduceto}[2]{\ensuremath{#1 \longmapsto^{*} #2}}
\newcommand{\transitivelyreducetoD}[2]{
	\ensuremath{#1 \longmapsto_{\LDMachine}^{*} #2}}
\newcommand{\transitivelyreducetoUD}[2]{
	\ensuremath{#1 \longmapsto_{\LUDMachine}^{*} #2}}
\newcommand{\reduceto}[2]{\ensuremath{#1 \longmapsto #2}}
\newcommand{\reducetoR}[3]{\ensuremath{#2 \longmapsto_{\CMachine{#1}} #3}}
\newcommand{\reducetoD}[2]{\reducetoR{\BLD}{#1}{#2}}
\newcommand{\reducetoUD}[2]{\reducetoR{\BLUD}{#1}{#2}}
\newcommand{\reducetoS}[3]{\ensuremath{#2 \longmapsto_{\SMachine{#1}} #3}}
\newcommand{\evalto}[2]{\ensuremath{\mathrm{eval}(#1)=#2}}
\newcommand{\withmachineevalto}[3]{\ensuremath{\mathrm{eval}_{#1}(#2)=#3}}
\newcommand{\evaltoR}[3]{\ensuremath{\mathrm{eval}_{\CMachine{#1}}(#2)=#3}}
\newcommand{\evaltoD}[2]{\evaltoR{\BLD}{#1}{#2}}
\newcommand{\evaltoUD}[2]{\evaltoR{\BLUD}{#1}{#2}}
\newcommand{\evaltoS}[3]{\ensuremath{\mathrm{eval}_{\SMachine{#1}}(#2)=#3}}
\newcommand{\compatibletailhead}[2]{\ensuremath{#1\sim#2}}
\newcommand{\goodgap}[1]{\ensuremath{\mathrm{good}(#1)}}
\newcommand{\compileto}[4]{\expressiontyping{#1}{#2\rightsquigarrow#3}{#4}}
\newcommand{\machineequiv}[2]{
	\ensuremath{
		\withmachineevalto{#1}{e}{o}	
		\text{ if and only if }
		\withmachineevalto{#2}{e}{o}
		\text{ for all }
		\expressiontyping{\emptyset}{e}{T}
		\text{ and }
		\valuetyping{o}{T}
	}}
\newcommand{\bisimE}[3]{\ensuremath{#1 \vdash #2 \approx #3}}
\newcommand{\bisimv}[3]{\valuetyping{#1 \approx #2}{#3}}
\newcommand{\bisimr}[3]{\valuetyping{#1 \approx #2}{#3}}
\newcommand{\bisimF}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisimc}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisimK}[4]{\casttyping{#1 \approx #2}{#3}{#4}}
\newcommand{\bisims}[3]{\valuetyping{\ensuremath{#1 \approx #2}}{#3}}

@@

\todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
\todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
sentence. It might be appopriate to cite it elsewhere in the paper. Also,
there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
\todo[inline]{KC: How about citing the origin of the proxy-based approach when we talk
about the CPSed even-odd example?
I am confused about which paper to cite. \cite{herman2010space} seems to be citing
\cite{findler2002contracts} for the proxy-based approach of casting function.
Here is the relevant sentences from \cite{herman2010space}:
``In general, it is not possible to check if an untyped function satisfies a
particular static type. A natural solution is to wrap the function in a proxy that, whenever
it is applied, casts its argument and result values appropriately, ensuring that the function
is only observed with its expected type. This proxy-based approach was formalized by Findler
and Felleisen [15] ...''
I am \textit{not} trying to say I don't believe in your statements about the origins of
the proxy-based approach and blame tracking in functions.
I want to know whether \citet{herman2010space} is citing the right paper.
Maybe both papers came up independently with a similar idea but \cite{findler2002contracts}
is more related to our work.
}
\todo[inline]{JS: In the above you've lumped proxy-based and blame
  tracking together, which is incorrect. AFAIK,
  \cite{findler2002contracts} is the origin of blame tracking. AFAIK,
  \citet{Breazu-Tannen:1990vc} is the origin of proxy-based casts.
  You can read both papers for yourself and be the judge.  BTW, TAPL
  (section 15.6) cites Breazu-Tannen.  So \citet{herman2010space}
  cited the wrong paper for function proxies, perhaps because they
  didn't know about \citet{Breazu-Tannen:1990vc}. Also,
  \cite{findler2002contracts} should have cited
  \citet{Breazu-Tannen:1990vc} but did not. Perhaps because they did
  not consider that papers about ``casts'' to be closely related to
  their paper about ``contracts''.  Or perhaps they too did not know
  about \citet{Breazu-Tannen:1990vc}.  Authors make mistakes all the
  time regarding related work, and this is just yet another example of
  that. For that matter, I should have cited
  \citet{Breazu-Tannen:1990vc} in \citet{siek2006gradual} but did not,
  probably because I had learned about it from TAPL and therefore
  thought it was so standard that it didn't need a citation.  But it
  would have been better for me to cite it.}

@@

\todo[inline]{KC: in the next paragraph I cite \cite{breazu1991inheritance}}
Continuations are not the only place where casts can accumulate.
Consider a variant of the above program written in
continuation-passing style.  Here, both functions returns
\lstinline|Bool| so there is no implicit cast in tail position.
% However, the argument \lstinline|k| is wrapped in a cast in each
% recursive call because the type of \lstinline|k| is less precise in
% \lstinline|even?| than it is in \lstinline|odd?|.
However, the argument \lstinline|k| is casted in each
recursive call because the type of \lstinline|k| is less precise in
\lstinline|even?| than it is in \lstinline|odd?|. 
Every time a function is casted we record a pieces of
cast information for the input and another piece for
the output, following the approach in \cite{breazu1991inheritance}
and \cite{Breazu-Tannen:1990vc},
so the space complexity is again linear.
\begin{lstlisting}
(define (even? [n : Int] [k : (-> $\star$ Bool)]) : Bool
  (if (= n 0) (k #t) (odd? (- n 1) k)))
(define (odd? [n : Int] [k : (-> Bool Bool)]) : Bool
  (if (= n 0) (k #f) (even? (- n 1) k)))
\end{lstlisting}
These example programs are adapted from those of \cite{herman2010space}.
We direct readers to their work for more examples and a detailed explanation.

@@

Of course, a space-efficient cast representation must be proved
correct. That is, a language implementation that uses space-efficient
casts should give the same output as the language semantics. Our
generic CEK machine comes with generic theorems mechanized in
the Agda proof assistant~\citep{norell2008dependently}
(Section~\ref{sec:framework}) that researchers can use to prove a cast
representation correct.  We believe this framework can reduce the
burden of proving correctness theorems and help people focus on the
cast representations. As a demonstration, we apply the framework to
Lazy UD coercions in normal form~\citep{Siek:2015:BCT:2737924.2737968}
and Lazy UD threesomes~\citep{Siek:2010:TWB:1706299.1706342}. We
believe the framework is also applicable to other cast
representations. The framework and demonstrations are available at the
following URL:
\[\text{\urlFrameworkAndIllustration}\]

@@

\todo[inline]{JS: add a sentence that summarizes this section,
  mentioning the topics of the two subsections.}
\todo[inline]{KC: fixed. I want to move this section to the end
of the paper, how do you think?}

In this section we review publications that contribute dynamic semantics
applicable to a variety of cast representations
(Subsection~\ref{subsec:parameterized-dynamics}),
proofs of correctness of cast representations
(Subsection~\ref{subsec:related-work-other-proofs}),
and relationship between hypercoercions and other cast representations
(Subsection~\ref{subsec:related-work-other-cast-reprs}).

\subsection{Dynamics semantics parameterized over cast representations}
\label{subsec:parameterized-dynamics}

\todo[inline]{KC: how can I forget the interpretation paper!}
\cite{siek2012interpretations} presents a definitional interpreter
and a variant of the ECD abstract machine \citep{siek2012ECD}.
Both systems are parameterized over 4 flavors of coercions in normal
forms: Lazy UD, Lazy D, Eager UD, Eager D.

\citet{garcia2014deriving} proves the definitional interpreter
in \cite{siek2012interpretations}
is equivalent to the ECD machine in the same paper,
which was left as a conjecture. 
They claim that their system ``can be generalised for other choices
of dynamic semantics by applying the correspondence described 
through the paper starting with a different set of coercion artefacts.''.
It is unclear to us whether their system is just applicable
to other flavor of coercions or also to other cast representations.

\todo[inline]{JS: The above is too short of a description of that related
work.}
\todo[inline]{KC: I am actually very confused by \citet{garcia2014deriving}.
They stated that ``Theorems 8.1 and 8.3 can be generalised for other choices
of dynamic semantics by applying the correspondence described
through the paper starting with a different set of coercion artefacts.''.
However they didn't give a generalization and it is unclear to me over what
their system is parameterized (cast representations? apply-coercion and seq?.}
\todo[inline]{JS: your comment above says what you should say
  (except the part about your confusion). Say it in a matter-of-fact
way, and not a derogitory way.}
\todo[inline]{KC: updated.}

@@

\subsection{Correctness of cast representations}
\label{subsec:related-work-other-proofs}

@@

\cite{Siek:2015:BCT:2737924.2737968} proves the correctness
of \LUD\ coercions in normal form. Their approach is similar to
that of \citet{Siek:2010:TWB:1706299.1706342}. They defines
three calculi (i.e. $\lambda B$ and $\lambda C$ and $\lambda S$). 
$\lambda B$ is the blame calculus. 
$\lambda C$ uses coercions but doesn't normalize coercions
so is not space-efficient. $\lambda S$ uses coercions in normal form
and is space-efficient. To establish the correctness of
their cast representation,
they prove a bisimulation relating $\lambda B$ to $\lambda C$
and a bisimulation relating $\lambda C$ to $\lambda S$.

Inspired by the approaches of \cite{Siek:2010:TWB:1706299.1706342}
and \cite{Siek:2015:BCT:2737924.2737968}, 
we also use the bisimulation technique. But our bisimulation have an
important difference. Our bisimulation relation, unlike theirs, does
not cover all possible states in the reduction. Instead, we ask both 
sides of the bisimulation to reduce several steps before recovering
the bisimulation relation (compare our Lemma~\ref{lem:weak-bisimulation}
with Lemma~8 in \cite{Siek:2010:TWB:1706299.1706342}
and Proposition~16 in \cite{Siek:2015:BCT:2737924.2737968}).
This decision simplifies the bisimulation relation (Fig.~\ref{fig:bisim-SC-D})
(compared to Figure~6 in \cite{Siek:2010:TWB:1706299.1706342} and
Figure~6 in \cite{Siek:2015:BCT:2737924.2737968}).
In particular, the function application case is a congruence
(hence not shown in the figure) in our bisimulation relation
but requires special rules in theirs.

\todo[inline]{JS: there is a least one interesting difference regarding
  the bisimulation: your lemma 3 has an ``upto reduction'' flavor to it
  which makes your $\approx$ relation simpler. }
\todo[inline]{KC: updated.}

\subsection{Other Cast Representations}
\label{subsec:related-work-other-cast-reprs}

Hypercoercions is inspired by coercions in normal form and supercoercions
and ends up having a symmetrical definition similar to threesomes.

@@

\todo[inline]{KC: is this the right place to mention that in Agda
code we use de Bruijn indexes?}

@@

\caption{Bisimulation between \CBMachine\ and \SMachine{C}. It is the
  smallest congruence relation containing the shown rules. Everything
  to the left of $\approx$ is in \CMachine{B} and everything to the
  right is in \SMachine{C}.}
\label{fig:bisim-SC-D}
\end{figure}

@@

\todo[inline]{JS: There should be some text regarding the following
two theorems.}
\todo[inline]{KC: Fixed.}

Lemma~\ref{lem:weak-bisimulation} implies that if a \CMachine{B} state $s_1$ transitions to a 
final state $s_2$ and \bisims{s_1}{s'_1}{T}, the state $s_1'$
will transition to a final state $s_2'$ that holds the same observable as $s_1'$. 
Instantiating Lemma~\ref{lem:weak-bisimulation} with Lazy D and Lazy UD blame strategy leads
to the next two theorems.

\begin{theorem}[Correctness of Lazy D \SMachine{C}]
	\label{thm:SD-equiv}
	Suppose $C$ is a Lazy D Cast ADT.
	\[
	\machineequiv{\CBMachine}{\SMachine{C}}
	\]
\end{theorem}

\begin{theorem}[Correctness of Lazy UD \SMachine{C}]
	\label{thm:SUD-equiv}
	Suppose $C$ is a Lazy UD Cast ADT.
	\[
	\machineequiv{\CBMachine}{\SMachine{C}}
	\]
\end{theorem}

@@

Subsection~\ref{sec:LazyUD-Hypercoercions} implements the \CastADT{}
with the \LUD{} hypercoercions and proves that \LUD{} hypercoercions is
a Lazy UD Cast ADT.  Subsection~\ref{sec:LazyUD-Hypercoercions} does
the same for \LD{}.  Finally, we argue in
Subsection~\ref{sec:hypercoercions-compact} that hypercoercions
consume less space than coercions in normal form and hence are more
suitable for implementation.

\todo[inline]{JS: I'd recommend moving this subsection before that of
  LazyD because a reader is more likely to be familiar with Lazy UD.}
\todo[inline]{KC: Updated.}

% Hypercoercions for the \LUD\ blame tracking strategy have the same syntax
% as for \LD\ (\figref{fig:hypercoercion}), but the definitions of $\id{T}$ and
% $\translate{\ccast{S}{l}{T}}$ and $\compose{c}{c}$, differ from \LD. Here 
% composition $\compose{c_1}{c_2}$ makes the usual assumption that the
% target type of $c_1$ matches the source type of $c_2$. 
% %
The definition of composition for \LUD\ is particularly straightforward.
The first two lines say that \hcci\ acts as the identity on both the left
and right.
The third line handles the case when both hypercoercions have three parts. 
%
The first three lines of the middle composition $m \fatsemi t \fatsemi h 
\fatsemi m$ function match its arguments in sequential order to determine which 
label to blame. The forth and last line is straightforward recursion.

\todo[inline]{KC: I need a better name for \compatibletailhead{t}{h},
  any suggestion from Jeremy?}
\todo[inline]{JS: how about $\sim$}
\todo[inline]{KC: sounds good}

	\fbox{$m \fatsemi t \fatsemi h \fatsemi m = m$}
	\[
	\begin{array}{rccccclclr}
	\hcmfail{l} 
	& \fatsemi & t
	& \fatsemi & h
	& \fatsemi & m_2
	& = & \hcmfail{l} \\
	m_1
	& \fatsemi & \hcti{G}
	& \fatsemi & \hchp{H}{l}
	& \fatsemi & m_2
	& = & \hcmfail{l}
	& \sidecond{G \neq H \text{ and } \forall l. m_1 \neq \hcmfail{l}} \\
	m_1
	& \fatsemi & t
	& \fatsemi & h
	& \fatsemi & \hcmfail{l}
	& = & \hcmfail{l}
	& \sidecond{\compatibletailhead{t}{h}
		\text{ and } \forall l. m_1 \neq \hcmfail{l}} \\
	m_1
	& \fatsemi & t
	& \fatsemi & h
	& \fatsemi & m_2
	& = & m_1 \fatsemi m_2
	& \quad \sidecond{
		\forall l. m_2 \neq \hcmfail{l}
		\text{ and } \compatibletailhead{t}{h}
		\text{ and } \forall l. m_1 \neq \hcmfail{l}} \\
	\end{array}
	\]

\todo[inline]{KC: should we cite the place where ``Prior presentations'' locate?}
The translation function \translate{\ccast{S}{l}{T}} is defined in 
\figref{fig:LazyUD-Hypercoercions-translation}.  Prior
presentations of this function do not use auxiliary functions, as we
do here. The reason that we introduce the auxiliary functions
$\mathrm{castToDyn}$ and $\mathrm{castFromDyn}$, is to ensure that each of them 
is structurally recursive, which makes them straightforward to define in
Agda.

@@

Hypercoercions for the \LD\ blame tracking strategy have the same syntax
as for \LUD\ (\figref{fig:hypercoercion}), but the definitions of $\id{T}$ and
$\translate{\ccast{S}{l}{T}}$ and $\compose{c}{c}$ differ from \LUD.
% Here composition $\compose{c_1}{c_2}$ makes the usual assumption that the
% target type of $c_1$ matches the source type of $c_2$. 
%
\figref{fig:LazyD-Hypercoercions-composition} defines the composition
operator \compose{c}{c} for \LD\ hypercoercions and
\figref{fig:aux-hypercoercion-composition} defines some auxilliary
predicates and functions.
